### 2023-11-20 main.tex
''

\begin{remark}[Interpretation the elements $\Psi^{'}(\bm{\tau})$]
	For any given $\bm{\tau}\in \Omega^{'}$ we have that 
Indeed, arguing as in the previous proof, we have that

@@

\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$. Therefore, we have

@@

 Therefore, equation \eqref{interpretation-PsiP} follows. 

@@

@@

>>>>

\begin{remark}[Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution]
We argue as in the previous proof. For any given $\bm{\tau}\in \Omega^{'}$ we have that 

@@

\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have

@@

 where the above average is taken with respect to the non-equilibrium steady state of the process $\bm{\sigma}$. Equation \eqref{interpretation-PsiP} will be useful in the exact formula for the steady state. Given $\bm{\tau}$ as before, we can introduce $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ the number of occupied sites. Then we denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle is present. Finally, we call 
 	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}
Then, we have that
	\Psi(\bm{\tau})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})
	\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})
is marginal on $m$ sites of the steady state distribution.  

@@

\begin{remark}%[Correlation as the steady state of a $m$-chain ]

@@

 As a consequence, we can give a different interpretation to correlation computed in \eqref{exactCorrelations}. Consider the sites $(x_{k})_{k\in \{1,\ldots,m\}}$ and fix $(a_{k})_{k\in \{1,\ldots,m\}}$ introduced in Theorem \ref{thm-correlations}. We define a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$. We denote by $|\Psi_{m}\rangle$ the non-equilibrium steady state of this $m$-chain. Then, we have that the correlations computed in \eqref{exactCorrelations} can be written as
	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\Psi_{m}(a_{1},\ldots,a_{m})
This means that we can define a mapping between the $m$-point correlation of chain of length $L$ and the non-equilibrium steady state of a chain of length $m$. This mapping, 
